---
title: "Part 1 - Kera"
output: html_notebook
---
1. Show that the minimum order statistic converges in probability to 0. Hint: We know
the CDF of an exponential and how to find the CDF of the minimum order statistic.
Start with the probability you want to show from the definition of convergence in
probability to 0 (P(|Y(1) - 0| < e)) and take the limit as n goes to infinity and show
this is 1.

If a sequence of random variables, {Zn}, is such that P(|Zn−α| > e) approaches
zero as n approaches infinity, for any e > 0 and where α is some scalar, then Zn is
said to converge in probability to α.

lim n-> inf P(|Yn - c| >= e) = 0
lim n-> inf P(|Yn - c| < e) = 1
c = 0
lim n-> inf P(|Yn| < e) = 1
Distribution of the minimum: n*fY(y)[1-FY(y)]^(n-1)
lim n-> inf P(|Yn| >= e) = 0



2. To visualize this we’ll simulate data and approximate the probability statement proven in the previous part.
(a) For a sample size of n = 1, generate N = 1000 data sets from an exp(1) distribution.
(b) For each data set, find the minimum value (for a sample of size 1 that will just be the value itself).
(c) Save these minimum values for plotting.

```{r}
#Part a
N <- 1000
Exp_Data_set <- c()
x <- 0
while(x < N){
  Exp_Data_set <- c(Exp_Data_set, rexp(1, rate = 1))
  x <- x + 1
}
#To reset x so the while loop can run again
x <- 0

Exp_Data_Matrix <- cbind(Exp_Data_set)

#Part b
Exp_Min_Data <- c()
while(x < N){
  Exp_Min_Data <- c(Exp_Min_Data, min(Exp_Data_Matrix[x + 1,]))
  x <- x + 1
}
x <- 0
Exp_Min_Data_Matrix <- cbind(Exp_Min_Data)

#Part c
Exp_Plot_Data_1 <- Exp_Min_Data_Matrix

```

3. Consider an epsilon of 0.05. Approximate the probability of interest (P(|Y(1) − 0| < epsilon)) using these 1000 simulated minimum values. (This is a Monte Carlo estimate of the probability.) Save this probability

```{r}
epsi <- 0.05


```

4. Repeat the above simulation and approximation of the probability of interest for n =2, 3, ..., 50

```{r}
Exp_Data <- c()
n <- 50
x <- 0
y <- 0

while(x < N * n){
  Exp_Data <- c(Exp_Data, rexp(1, rate = 1))
  x <- x + 1
}
x <- 0
y <- 0

Exp_Matrix <- matrix(Exp_Data, nrow = 1000)

Min_Matrix <- c()
Min_Data_50 <- c()

while(x < N){
  Min_Data_50 <- c(Min_Data_50, min(Exp_Matrix[x + 1,]))
  x <- x + 1
  #y <- y + 1
}
x <- 0
#y <- 0
#Min_Matrix <- cbind(Min_Data_50)

Plot_Data_50 <- Min_Matrix
```

5. Create a plot with the sample size on the x-axis and the probability of interest on the y-axis. All created plots should have titles and appropriate axis labels.

```{r}

```

6. In a comment explain how this plot can help someone understand convergence in probability to a constant.

```{r}

```

7. You should also have the 1000 values of the minimum for each n saved from above. Create a plot with the sample size on the x-axis and the values of the minimum on the y-axis. (You should have 1000 values plotted above n = 1, 1000 plotted above n = 2, etc.). All created plots should have titles and appropriate axis labels.

```{r}

```

8. In a comment explain how this plot can help someone understand convergence in probability to a constant.

```{r}

```

