---
title: "Part 1 - Kera"
output: html_notebook
---

2. To visualize this we’ll simulate data and approximate the probability statement proven in the previous part.
(a) For a sample size of n = 1, generate N = 1000 data sets from an exp(1) distribution.
(b) For each data set, find the minimum value (for a sample of size 1 that will just be the value itself).
(c) Save these minimum values for plotting.

```{r}
#Part a
N <- 1000
Exp_Data_set <- c()
x <- 0
while(x < N){
  Exp_Data_set <- c(Exp_Data_set, rexp(1, rate = 1))
  x <- x + 1
}
#To reset x so the while loop can run again
x <- 0

Exp_Data_Matrix <- cbind(Exp_Data_set)

#Part b
Exp_Min_Data <- c()
while(x < N){
  Exp_Min_Data <- c(Exp_Min_Data, min(Exp_Data_Matrix[x + 1,]))
  x <- x + 1
}
x <- 0
Exp_Min_Data_Matrix <- cbind(Exp_Min_Data)

#Part c
Exp_Plot_Data_1 <- Exp_Min_Data_Matrix

```

3. Consider an epsilon of 0.05. Approximate the probability of interest (P(|Y(1) − 0| < epsilon)) using these 1000 simulated minimum values. (This is a Monte Carlo estimate of the probability.) Save this probability

```{r}
epsi <- 0.05


```

4. Repeat the above simulation and approximation of the probability of interest for n =2, 3, ..., 50

```{r}
Exp_Data <- c()
n <- 50
x <- 0
y <- 0

while(x < N * n){
  Exp_Data <- c(Exp_Data, rexp(1, rate = 1))
  x <- x + 1
}
x <- 0
y <- 0

Exp_Matrix <- matrix(Exp_Data, nrow = 1000)

Min_Matrix <- c()
Min_Data_50 <- c()

while(x < N){
  Min_Data_50 <- c(Min_Data_50, min(Exp_Matrix[x + 1,]))
  x <- x + 1
  #y <- y + 1
}
x <- 0
#y <- 0
#Min_Matrix <- cbind(Min_Data_50)

Plot_Data_50 <- Min_Matrix
```

5. Create a plot with the sample size on the x-axis and the probability of interest on the y-axis. All created plots should have titles and appropriate axis labels.

```{r}

```

6. In a comment explain how this plot can help someone understand convergence in probability to a constant.

```{r}

```

7. You should also have the 1000 values of the minimum for each n saved from above. Create a plot with the sample size on the x-axis and the values of the minimum on the y-axis. (You should have 1000 values plotted above n = 1, 1000 plotted above n = 2, etc.). All created plots should have titles and appropriate axis labels.

```{r}

```

8. In a comment explain how this plot can help someone understand convergence in probability to a constant.

```{r}

```

