---
title: "Part 1 - Kera"
output: html_notebook
---

2. To visualize this we’ll simulate data and approximate the probability statement proven in the previous part.
(a) For a sample size of n = 1, generate N = 1000 data sets from an exp(1) distribution.
(b) For each data set, find the minimum value (for a sample of size 1 that will just be the value itself).
(c) Save these minimum values for plotting.

```{r}
N <- 1000
Exp_Data_set <- c()
x <- N
while(x >0){
x <- x-1
Exp_Data_set <- c(Exp_Data_set, rexp(1))
}
#print(Exp_Data_set)
```

3. Consider an epsilon of 0.05. Approximate the probability of interest (P(|Y(1) − 0| < epsilon)) using these 1000 simulated minimum values. (This is a Monte Carlo estimate of the probability.) Save this probability

```{r}

```

4. Repeat the above simulation and approximation of the probability of interest for n =2, 3, ..., 50

```{r}

```

5. Create a plot with the sample size on the x-axis and the probability of interest on the y-axis. All created plots should have titles and appropriate axis labels.

```{r}

```

6. In a comment explain how this plot can help someone understand convergence in probability to a constant.

```{r}

```

7. You should also have the 1000 values of the minimum for each n saved from above. Create a plot with the sample size on the x-axis and the values of the minimum on the y-axis. (You should have 1000 values plotted above n = 1, 1000 plotted above n = 2, etc.). All created plots should have titles and appropriate axis labels.

```{r}

```

8. In a comment explain how this plot can help someone understand convergence in probability to a constant.

```{r}

```

